State of the Practice for Lattice Boltzmann Method Software

### 2022-03-07 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
reviewed threats to validity

In our methodology one individual measures each package and the beginning and
ending of the measurement phase is separated by several months.  There is a
threat that the measurement may include unconscious biases, or the reviewers
judgement may drift over time.  In previous work \citep{SmithEtAl2016}, we
demonstrated that the measurement process is reasonably reproducible by having 5
products graded by a second reviewer. The ranking via this independent review
was almost identical to the original ranking. As long as each grader uses
consistent definitions, the relative comparisons in the AHP results will be
consistent between graders.

@@

Another data collection concern is the gap between measurement of Musubi and the
measurement of all other packages (Section~\ref{identifysoftware}).
Unfortunately we were not aware of the existence of Musubi until after the
primary data collection period was completed. This gap has a secondary effect
because it caused a mismatch between the time of manual and automated data
collection (Section~\ref{repmetrics}).  With time and resource constraints we
could not redo the manual measurement, but we did update the automated measures
(like the number of files, LOC, etc.) when Musubi was added.

>>>>

In our methodology, one individual measures each package and the beginning and
ending of the measurement phase is separated by several months.  There is a
threat that the measurement may be affected by unconscious biases, or the reviewers judgement may drift over time.  In previous work \citep{SmithEtAl2016}, we demonstrated that the measurement process is reasonably reproducible by having five products graded by a second reviewer. The ranking via this independent review was almost identical to the original ranking. As long as each grader uses
consistent definitions, the relative comparisons in the AHP results will be
consistent between graders.

@@

Another data collection concern is the gap between the measurement of Musubi and the measurement of all other packages (Section~\ref{identifysoftware}).
Unfortunately we were not aware of the existence of Musubi until after the
primary data collection period was completed. This gap has a secondary effect
because it caused a mismatch between the time of manual and automated data
collection (Section~\ref{repmetrics}).  With time and resource constraints we
could not redo the manual measurement, but we did update the automated measures
(like the number of files, LOC, etc.) when Musubi was added.
